---
title: ""
format: 
  html:
    theme: custom.scss
    embed-resources: true
    page-layout: article
execute:
  echo: false
  warning: false
---


::: columns
::: {.column width="28%"}
<center><a href='https://www.linkedin.com/in/michal-kinel/' target='_blank'> ![](https://avatars.githubusercontent.com/u/36136546?v=4){width="80%" style="border-radius: 50%;"}</center>

</a>


### Contact

<span><a href='https://www.linkedin.com/in/michal-kinel/' target='_blank'><i class="fa-brands fa-linkedin fa-xl" style="color: #1d4f67;"></i></a> michal-kinel </span> <br><br>
<span><a href='mailto:michal.kinel@gmail.com' target='_blank'><i class="fa-solid fa-envelope fa-xl" style="color: #1d4f67;"></i></a> michal.kinel@gmail.com </span> <br><br>
<span><a href='https://wa.me/34634469309' target='_blank'><i class="fa-solid fa-mobile fa-xl" style="color: #1d4f67;"></i></a> +34 634 469 309 </span> <br><br>
<span><a href='https://github.com/michal0091' target='_blank'><i class="fab fa-github fa-xl" style="color: #1d4f67;"></i></a> michal0091 </span>

### Idiomas

**Polaco:** Nativo <br> **Español:** Nativo <br> **Inglés:** Alto <br> **Alemán:** Básico

### Habilidades técnicas

#### Data Science

<i class="fa-brands fa-r-project" style="color: #1d4f67;"></i> `R`<br> 
<i class="fa-solid fa-database" style="color: #1d4f67;"></i> `SQL` <br>
<i class="fa-brands fa-python" style="color: #1d4f67;"></i> `Python` <br>

#### Sistemas operativos

<i class="fa-brands fa-ubuntu" style="color: #1d4f67;"></i> `Ubuntu` <br>
<i class="fa-brands fa-windows" style="color: #1d4f67;"></i> `Windows` <br>

#### Herramientas

<i class="fas fa-code-branch" style="color: #1d4f67;"></i> `Git` <br>
<i class="fab fa-github" style="color: #1d4f67;"></i> `GitHub` <br>
<i class="fa-brands fa-docker" style="color: #1d4f67;"></i> `Docker` <br>
<i class="fa-solid fa-font" style="color: #1d4f67;"></i> `LaTeX` <br>
<i class="fa-brands fa-microsoft" style="color: #1d4f67;"></i> `Azure` <br>

#### Frameworks

<i class="fab fa-markdown" style="color: #1d4f67;"></i> `RMarkdown / Quarto`<br>
<i class="fa-brands fa-r-project" style="color: #1d4f67;"></i> `Shiny` <br>
<i class="fab fa-markdown" style="color: #1d4f67;"></i> `Markdown` <br>

:::

::: {.column width="5%"}
:::

::: {.column width="67%"}


# Michal Kinel

```{r}
#| include: false
library(data.table)
library(dplyr)

cv_dt <- fread("mmk_cv_data.csv")


# load libraries
library(data.table)
library(dplyr)

col_br <- function(col){
  dplyr::if_else(
    !is.na(col) & col != "N/A|NA", 
    paste0(col),
    ""
  )
}

col_br_loc <- function(col){
  dplyr::if_else(
    !is.na(col) & col != "N/A|NA", 
    paste0('<span style="color: #1d4f67;"> <br><b><i>', col, " </i></b></span>"),
    ""
  )
}

col_br_title <- function(col){
  dplyr::if_else(
    !is.na(col) & col != "N/A|NA", 
    paste0('<span style="color: #556a99; font-size: larger"><b>', col, " </b></span><br>"),
    ""
  )
}

create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", NA_character_, loc)) |>
    dplyr::filter(in_resume == TRUE, section == section_name) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Actualidad <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "{col_br_title(title)} {col_br(institution)} {col_br(description_1)} {col_br_loc(loc)}"),
      .after = date
    ) |>
    dplyr::select(c(date, main_text)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text) |> 
    gt::cols_width(date ~ gt::pct(10))
}

```



## <i class="fa-solid fa-suitcase"></i> Experiencia Laboral

```{r}
cv_dt %>% 
  create_section("working_experience")

```

<br> 

## <i class="fa-solid fa-graduation-cap"></i> Educación

```{r}
cv_dt %>% 
  create_section("education")
```



## <i class="fa-solid fa-certificate"></i> Certificaciones y Cursos Adicionales

```{r}
cv_dt %>% 
  create_section("certificates_courses")
```


## <i class="fa-solid fa-book"></i> Publicaciones

```{r}
cv_dt %>% 
  create_section("publications")
```


:::
:::



```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```